Models of lens candidates from Space Warps CFHTLS

### 2016-07-28 paper2.tex
rE comparison figure
new spaghetti images, updates of all others
minor typos

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

@@

\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
  Space Warps CFHTLS}

@@

The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
tendency to be too shallow.  Allowing smaller mass tiles in the
central region, thus allowing the pass profile to rise more steeply
near the centre, was suggested as a possible cure.

@@

\begin{figure}
  \caption{}
  \label{fig:parameter}
\end{figure}

>>>>

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
%	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
%        \includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
}

@@

\title[Lens models for Space Warps CFHTLS]{Models of lens candidates from
  Space Warps CFHTLS}

@@

The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
tendency to be too shallow.  Allowing smaller mass tiles in the
central region, thus allowing the mass profile to rise more steeply
near the centre, was suggested as a possible cure.

@@

Preliminary results on recovery of Einstein radii are shown in
Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
  model-fitting.}

\begin{figure}
  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
  \caption{Comparison of Einstein radii. {\em To be extended.}}
  \label{fig:parameter}
\end{figure}
